---
title: "Hands-on dataanalysis in R"
author: 'Flow-number: 86'
date: "1/18/2022"
output: word_document
---


Ps. This code assumes the dataset is already in your working directory
```{r}
ID86 <- read.csv("data00.csv")
head(ID86, 2)
```

# Question 1a

Checking for all unique days of the week
```{r}
unique(ID86$Day)
```

Renaming Tuesday and Friday
```{r}
ID86$Day[ID86$Day=="Tuesday"] <-"Tues"
ID86$Day[ID86$Day=="Friday"] <-"Fri"
```

Sub-setting for Tuesday evening in the whole of April and stored in Q1a
```{r}
April <- ID86[grepl("Apr", ID86$Date),]
Tuesday <- subset(April, April$Day=="Tues")
Q1_a <- subset(Tuesday,Tuesday$Daytime=="night")

sum(Q1_a$ItemsOrdered)
#The number of products purchased on Tuesday evenings throughout April is 22
```

# Question 1b
```{r}
nrow(Q1_a)
#The number of purchase events on Tuesday evening throughout April is 6
```

# Question 2a
```{r}
One_product <- subset(ID86, ID86$ItemsOrdered=="1")
nrow(One_product)
#the number of times 1 product was bought is 60
```

# Question 2b
```{r}
max(ID86$ItemsOrdered)
#The highest amount of bought products in 1 single order is 11
```

# Question 2c
```{r}
plot(ID86$ItemsOrdered, main = "Items Ordered")
hist(ID86$ItemsOrdered, main = "Items Ordered")
```

# Question 3a
```{r}
men <- subset(ID86, ID86$Gender=="Male")
men_total <- sum(men$ItemsOrdered)
men_total

women <- subset(ID86, ID86$Gender=="Female")
women_total <- sum(women$ItemsOrdered)
women_total


product_difference <- men_total- women_total
product_difference 
#men buy 267 less than the women 
```

# Question 3b
Calculating the average for both men and women
```{r}
avg_men <- mean(men$ItemsOrdered)
avg_men

avg_women <- mean(women$ItemsOrdered)
avg_women
```

Average difference for both men and women
```{r}
avg_difference <- avg_men-avg_women
avg_difference
```

Converting the avg_difference to percentage
```{r}
avg_difference*100       
#The difference is significant.
```

# Question 3c
Total purchased by men
```{r}
men_purchase <- sum(men$TotalAmountPaid)
men_purchase
```

Total purchased by women
```{r}
women_purchased <- sum(women$TotalAmountPaid)
women_purchased
```

Purchased difference for men and women
```{r}
purchased_difference <- men_purchase - women_purchased
purchased_difference
#The purchase difference between men and women is -12263.31 
```
# Question 4
Tabulating the revenue by weekday
```{r}
day_revenue <- aggregate(ID86$TotalAmountPaid, by=list(weekday=ID86$Day),FUN =sum)
class(day_revenue)

highest_revenue <- subset(day_revenue, day_revenue$x==max(day_revenue$x))

highest_revenue$x
#The highest revenue

highest_revenue$weekday 
#The day with the highest revenue is Saturday
```
